Redundant calibration as a complex optimization problem

### 2017-01-03 paper.tex
still fixing section 6

\section{Results}

@@

\subsection{Alternating Direction Implicit Method}

>>>>

\section{Results}
In this section we compare the computational complexity of the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. We restrict ourselves to comparing the most 
expensive operation of the two methods namely, computing the inverse of the Hessian (or modified Hessian in the case of LM). It becomes trivial to rate these two 
algorithms relative to each other once the computational complexity of the inverse operation is known.

In Section~\ref{sec:adi} we re-derive the ADI method presented in \citet{Marthi2014}. In \citet{Marthi2014} the ADI method is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught. When derived in this way, its relation to the recent works \citep{Salvini2014,Smirnov2015} are unclear.
We use a similar approach to the diagonal approximate method proposed in \citet{Smirnov2015} to show that the ADI algorithm presented in \citet{Marthi2014} is in fact redundant 
StEfCal.

@@

\subsection{Alternating Direction Implicit Method}
\label{sec:adi}
